\documentclass{resume}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Mohammad Heydari} 
\address{1591 Lycée Place, Ottawa, ON, K1G 4A7 \\ +1 (613) 203 4437} 
\address{moheydari1997@gmail.com \\ linkedin.com/in/mmheydari97 \\ github.com/mmheydari97}

\begin{document}

\begin{rSection}{OBJECTIVE}
Python Developer with expertise in \textbf{data engineering} and \textbf{ETL processes}. Strong background in \textbf{Python development} using \textbf{pandas} and \textbf{NumPy} for data transformation. Experienced in \textbf{API development} with \textbf{FastAPI} and \textbf{database management} with \textbf{SQL/NoSQL}. Proven track record of successfully \textbf{migrating legacy systems} to efficient Python-based implementations with improved performance.
\end{rSection}


\begin{rSection}{EXPERIENCE}

\textbf{Analytics Engineer} \hfill \textit{February 2025 - Present}\\
Revolution Data Platforms \hfill \textit{Ottawa, Canada}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Developed a real-time customer service call management system using \textbf{Python}, \textbf{FastAPI}, and \textbf{WebSockets}, building end-to-end data processing pipelines for voice communication.
    \item Implemented a prototype application for voice memo transcription with \textbf{structured data extraction} and automated task management based on content severity.
    \item Optimized multi-class text classification through \textbf{prompt engineering} and \textbf{k-fold validation}, significantly improving model performance.
    \item Enhanced data quality through efficient \textbf{web scraping}, \textbf{data transformation}, and \textbf{preprocessing techniques} in Python.
 \end{itemize}
 
\textbf{Software Engineer} \hfill \textit{January 2023 - August 2024}\\
Paphus Solutions \hfill \textit{Ottawa, Canada}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Successfully migrated a Unity-based Android application to WebGL, implementing asynchronous connection management and data handling, demonstrating strong system migration capabilities.
    \item Integrated Python-based analytics pipelines with cloud services, enhancing real-time data processing through optimized ETL workflows.
    \item Developed chatbot APIs across multiple platforms using Python and RESTful services, improving user engagement through data-driven insights.
    \item Optimized deep learning models for custom question-answering, focusing on efficient data processing and query handling.
 \end{itemize}
 
\textbf{Course Instructor} \hfill \textit{September 2022 - December 2022}\\
Carleton University \hfill \textit{Ottawa, Canada}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Delivered comprehensive Python programming workshops focusing on data manipulation, pandas, and ETL concepts for real-world applications.
    \item Guided students in implementing ER diagrams and SQL for practical database solutions, emphasizing data integrity and efficient query optimization.
 \end{itemize}

\textbf{Graduate Research Assistant} \hfill \textit{January 2021 - November 2022}\\
Carleton University \hfill \textit{Ottawa, Canada}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Developed a Python-based data generation and transformation pipeline, optimizing ETL processes for deep learning models in research applications.
    \item Designed custom data preprocessing workflows and performance metrics for efficient data analysis and model evaluation.
 \end{itemize}

\textbf{Undergraduate Research Assistant} \hfill \textit{February 2018 - December 2020}\\
Amirkabir University \hfill \textit{Tehran, Iran}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Developed a Python-based anomaly detection system for time-series data processing, implementing efficient data transformation and feature extraction techniques.
    \item Created simulation frameworks for generating and validating synthetic data, enhancing model training and evaluation methodologies.
 \end{itemize}

\end{rSection}

\begin{rSection}{Education}

{\bf M.Sc. in Computer Science (Specialization in Data Science)}  \hfill {\textit{January 2021 - November 2022}}\\
{Carleton University} \hfill \textit{Ottawa, Canada}
\\
\\
{\bf B.Sc. in Computer Engineering} \hfill {\textit{September 2015 - December 2020}}\\
Amirkabir University \hfill \textit{Tehran, Iran}

\end{rSection}

\begin{rSection}{PROJECTS}
\begin{itemize}

\item \textbf{Fine-Tuning and Local RAG for LLMs}\\ 
{Developed a lightweight data processing pipeline for Retrieval-Augmented Generation (RAG) using \textbf{Python}, enhancing information retrieval from domain-specific datasets. Implemented efficient data extraction and transformation techniques to optimize contextual search, demonstrating expertise in ETL processes for NLP applications.}

\item \textbf{Custom Information Retrieval System}\\ 
{Built a search engine from scratch in \textbf{Python}, implementing data extraction, cleaning, and transformation pipelines for efficient text processing. Utilized \textbf{pandas} for data manipulation and designed an indexing system to improve search accuracy for large document collections.}

\item \textbf{NLP-Driven Sentiment Analysis}\\ 
{Developed a Python-based ETL pipeline for processing textual data using \textbf{pandas} and \textbf{NumPy}. Created vectorized operations for efficient text feature extraction, achieving 93.61\% accuracy in sentiment classification through optimized data transformation.}

\end{itemize}
\end{rSection}

\begin{rSection}{SKILLS}

\begin{itemize}
    \item Strong proficiency in \textbf{Python} development with expertise in \textbf{pandas}, \textbf{NumPy}, and \textbf{scikit-learn} for implementing efficient ETL pipelines and data transformation workflows.
    
    \item Extensive experience in \textbf{data engineering} and \textbf{database management} with both SQL (PostgreSQL, MySQL) and NoSQL solutions for optimized data storage and retrieval.
    
    \item Demonstrated ability in \textbf{API development} using \textbf{FastAPI}, \textbf{Flask}, and \textbf{Django} for robust back-end systems that handle complex data processing.
    
    \item Proven track record in \textbf{system migration} projects, successfully transitioning legacy codebases to modern Python implementations with improved performance.
    
    \item Proficient in \textbf{cloud-based data solutions} on AWS and Azure, with experience optimizing data processing pipelines in distributed environments.
\end{itemize}

\end{rSection}

\begin{rSection}{LANGUAGES \& CERTIFICATIONS}
\textbf{Programming:} Python, SQL, Java, C\# \hfill \textbf{Languages:} English (Fluent), French (Intermediate), Persian (Native)\\
\textbf{Certifications:} DataCamp Data Scientist with Python, Coursera GANs Specialization
\end{rSection}

\end{document}